Juliacon Proceedings in Quarto

### 2023-11-15 template.tex
got rid of number at the end of abstract
uf

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

% Abstract
\begin{abstract}
This document is a Quarto template demonstrating the
\texttt{juliacon-proceedings} format.
\end{abstract}

@@

% Hypersetup
\hypersetup{
    pdftitle = {Juliacon Proceedings in Quarto},
    pdfsubject = {JuliaCon 2023 Proceedings},
    pdfauthor = {Patrick Altmeyer},
    pdfkeywords = {Template, Demo, Quarto, JuliaCon},
}

@@

\section{Introduction}\label{sec-intro}

@@

x = -3.0:0.01:3.0
y = rand(length(x))
plot(x, y)
\end{verbatim}

>>>>

\usepackage{amsmath,amssymb}
\usepackage{setspace}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

% Abstract
\begin{abstract}

This document is a template demonstrating the
\texttt{juliacon-proceedings} format. It is a standard Quarto document
composed of Markdown, LaTeX and code chunks. It is rendered to PDF and
HTML. The PDF is rendered using the \texttt{juliacon-proceedings-pdf}
format, which is based on the \texttt{juliacon-proceedings} LaTeX class.
The HTML is rendered using the \texttt{juliacon-proceedings-html}
format, which is based on the \texttt{juliacon-proceedings} HTML
template.
\end{abstract}

@@

% Hypersetup
\hypersetup{
    pdftitle = {Juliacon Proceedings in Quarto},
    pdfsubject = {JuliaCon \@year Proceedings},
    pdfauthor = {Patrick Altmeyer},
    pdfkeywords = {Template, Demo, Quarto, JuliaCon},
}

@@

\setstretch{1}
\section{Introduction}\label{sec-intro}

@@

x = -3.0:0.01:3.0
y = rand(length(x));
\end{verbatim}
